Novel lattice Boltzmann method for simulation of strongly shear thinning viscoelastic fluids

### 2024-06-22 NovelLBM.tex
Updates to revision

To understand the rheology of such complex liquids in non-trivial geometries, computer simulations are an invaluable tool.
While a number of numerical techniques have been developed, the simulation of viscoelastic liquids remains an involved subject \cite{Alves.2020}, in particular for high viscosity ratios.
A very popular simulation technique for Newtonian fluids is the Lattice Boltzmann method (LBM) \cite{Kruger_book} due to its simplicity and high parallelizability.
LBM has also been extended to viscoelastic situations, mainly in two \cite{ispolatov2002,wang2019,su2013,giraud1998,xie2018,dzanic2022,frank2006,zou2014,lee2017,dzanic2022_2,sedaghat2021,frantziskonis2011,qin2023,yoshino2008,papenkort2015,phillips2011,onishi2005} but occasionally also in three \cite{malaspinas2010,gupta2015,gupta2015_2,lallemand2003,ma2020,onishi2006,wang2020,dellar2014,su2013_2,wang2021,kuron2021,gupta2016} dimensions.
To alleviate stability problems, some of these works include an artificial diffusivity of the polymer stress \cite{malaspinas2010,ma2020,wang2020,wang2021}, or perform special decompositions of the stress tensor \cite{dzanic2022}.
Despite these improvements, however, none of these methods has been applied to very high viscosity ratio fluids which are often used as cell carrier fluids in lab experiments or technological applications.

@@

We introduce the ratio between the polymer and the solvent viscosity as
\begin{align}
	R_\eta = \frac{\eta_\text{p}}{\eta_\text{s}} = \frac{\eta_0-\eta_\infty}{\eta_\infty}		\label{eq:R_eta}
\end{align}
which we and others found to be an important parameter to determine numerical stability of LB simulations, especially if no artificial diffusivity is used \cite{malaspinas2010,dzanic2022_2}.
This ratio can similarly be defined for other models such as FENE-P or the inelastic, but shear-thinning Carreau-Yasuda model \cite{carreau1972, yasuda1979} using the zero-shear viscosity $\eta_0$ and the infinite-shear viscosity $\eta_\infty$.
For our alginate solution we obtain $R_\eta = \num{48.2\pm0.4e3}$, indicating that the solution viscosity at very low shear rates is more than four orders of magnitude larger than the solvent viscosity which represents a severe challenge to standard numerical algorithms.
That this characteristic is not unique to alginate, but is in fact a generic feature of cell carrier fluids used in bioprinting is shown in table~\ref{tab:bioinks} where rheological data from various literature sources have been compiled into a single format to determine $R_\eta$.
The \SI{0.49}{\percent} methyl cellulose solution used in RT-DC measurements, in contrast, features a much lower value of $R_\eta = \num{18.7\pm0.4}$.

@@

\section{Existing LBM methods}
Since the early days of LBM, variants for viscoelastic fluids have been developed.
Keeping in mind our target geometries, we focus here on three-dimensional formulations.
The first approaches avoided an explicit modeling of a viscoelastic constitutive equation and simply modified the LB collision operator to obtain a basic viscoelastic fluid obeying Jeffery's model \cite{lallemand2003}. This can also be achieved by the introduction of a second local stress tensor \cite{dellar2014}.
More advanced approaches include the work of Onishi \textit{et al.} \cite{onishi2005, onishi2006} who considered a non-shear-thinning Oldroyd-B model using a microscopic Fokker-Planck equation for the polymer dumbbells.
The work of \cite{wang2020} solved the advection part of the model using a second LBM running in parallel to the Navier-Stokes LBM.
The same technique was used by \cite{malaspinas2010} and \cite{ma2020} for the Oldroyd-B and FENE-P models.
Later, hybrid schemes coupling an LB solver for the solvent to a finite-difference \cite{gupta2015_2, gupta2015, gupta2016} or finite-volume \cite{kuron2021} scheme for the polymer stress (or, alternatively, the polymer conformation) tensor were introduced.
To improve numerical stability, some authors propose the inclusion of an artificial diffusivity \cite{malaspinas2010,ma2020,wang2020,wang2021}, which introduces a small error compared to the analytical solution of the constitutive equation.
Others perform special decompositions of the stress tensor\cite{dzanic2022}.
Coupling of the resulting polymer stress to the Navier-Stokes LBM can be achieved via the inclusion of point forces or via a modification of the equilibrium populations.
Both methods have recently been compared in 2D \cite{dzanic2022_2}.

@@

The spatio-temporal dynamics of the polymer stress $\ma{\tau}$ is given by equation~(\ref{eq:polymerStress}) in the form of an advection-reaction equation.
We solve this equation by a finite-volume scheme running in parallel (with identical time step) to the LBM solver.\RR{ For this, the simulation volume is subdivided in $1\times1\times1$ (in LU) cubes centered around each lattice node. The average value of $\ma{\tau}$ within these volumes is takes as the value at the lattice node.}
Advection is handled using the corner transport upwind scheme \cite{kuron2021}.\RR{ The remaining derivatives are calculated using finite differences.}
At the walls\RR{, which coincide with the surfaces of the finite volumes}, a zero-flux boundary condition for the stress is used.
The source terms are integrated using the Euler method.

@@

We start by simulating the alginate and \SI{0.49}{\percent} methyl cellulose solutions with a viscosity ratio $R_\eta = \num{48.2e3}$ and $R_\eta = \num{18.7}$, respectively, in 2D planar Poiseuille flow.
In physical units the channel has a height of \SI{20}{\micro\meter} which are discretized with 41 LBM nodes.
For the viscosity shuffling, we set $\alpha_\text{s} = 1$ here and check different values further below.
Along the flow direction, the channel is periodic, and the flow is driven by a pressure gradient of \SI{-1e7}{\pascal\per\meter} for alginate and  approximately \SI{-1.2e7}{\pascal\per\meter} for methyl cellulose.
The velocity field is initialized with zero.
For methyl cellulose, we simulate the full temporal evolution with the polymers starting in the unstretched configuration.
In the case of alginate, we speed up the convergence and start from a situation in which the polymers are pre-stretched. For this we calculate $\tau_{xx}$ and $\tau_{xy}$ using equations~(\ref{eq:tau_xx}) and (\ref{eq:PTTDerivation2}) using the $\dot{\gamma}$ calculated from equation~(\ref{eq:semiAnalyticGD_3D}). The polymer stress is then initialized using these values.
After \num{2e9} LBM time steps for alginate and \num{5e6} LBM time steps for methyl cellulose corresponding to approximately \SI{1.6}{\milli\second} and \SI{2.4}{\second} of physical time, respectively, the simulation is stopped and the flow field $u(y)$ is compared to the semi-analytical solution.
As shown in figure~\ref{fig:2Dvel}, very good agreement is found.
The time evolution of the center-line velocity is shown in figure~\ref{fig:2DTimeEvolution} of the appendix.
For a quantitative assessment, we compute the L2 error as follows.
\begin{equation}
	e_\text{L2} = \sqrt{\frac{\sum_i\left[\vec{u_i} - \vec{u}\left(y_i\right)\right]^2}{\sum_i\vec{u}\left(y_i\right)^2}}
\end{equation}
Using the simulated velocities $\vec{u_i}$ and the semi-analytical results $\vec{u}$. This gives \num{9e-4} and \num{1e-3} for alginate and methyl cellulose, respectively.
The spatially resolved L1 error defined as follows is shown in figure~\ref{fig:2DvelErr} in the appendix.
\begin{equation}
	e_\text{L1} = \frac{\vec{u_i} - \vec{u}\left(y_i\right)}{\vec{u}\left(y_i\right)}
\end{equation}
These conclusions remain unchanged even when varying the pressure gradient, and thus the flow velocity, over many orders of magnitude as shown in figure~\ref{fig:pressureErr}~(a) of the appendix.
Similarly, the exact value of $\alpha_\text{s}$ does not matter as can be seen in figure~\ref{fig:ShuffleInPoiseuille}.

@@

Our next example is the RT-DC geometry in which cells from a reservoir are squeezed through a narrow observation channel \cite{Toepfner.2018, Fregin:2019gx} with a square cross-section of \qtyproduct{40x40}{\micro\meter}.
%$\SI{40}{\micro\meter} \times \SI{40}{\micro\meter}$.%Correctly typeset version, that compiles for Stephan.
For this simulation we use periodic boundary conditions and a constant body force corresponding to a pressure gradient of \SI{1e7}{\pascal\per\meter}.
In figure~\ref{fig:RT-DC}, we show the velocity profile, the von Mises stress and the shear component of the stress which is the relevant component if a local shear viscosity is to be defined.
There are three qualitative differences compared to a purely viscous fluid.
Directly after the inlet we find a region of low stress.
Due to the fast advection, the polymers, despite being inside the constriction, have not reacted to the increased fluid stress yet.
Similarly, directly after the constriction, the high stress inside the observation channel persists over a certain distance that is needed for the polymer stress to decay. If one would divide the stress in these two regions by the strain rate in an attempt to obtain a viscosity one would find a very low and a very high viscosity respectively. These can be outside the range of viscosities, that can be obtained through rheological measurements with the fluid. This effect is even more pronounced along the walls directly after the outlet. Here the viscosities obtained in this manner become negative. Due to the strain rate approaching $0$ at several locations within the simulation volume, this calculation often diverges. The clamped result can be seen in figure~\ref{fig:Nozzle/RT-DC_eta}. These discrepancies, especially the ones at the walls, show the breakdown of the viscosity interpretation in viscoelastic cases and signify the regions of interesting behavior. This also shows why viscoelastic simulations cannot always be replaced by purely viscous models and should be considered despite the high computational cost.

@@

	\section{Basics of Lattice-Boltzmann}\label{app:LBM}
	An excellent overview on Lattice-Boltzmann methods (LBM) can be found in the book by Krüger et al. on the subject \cite{Kruger_book}. Our implementation of the base algorithm mostly follows the book, though some implementation details differ. We mention the most important basics of LBM here and recommend the book for further reading.
	Instead of solving the Navier-Stokes equation LBM solves the Boltzmann equation which is a generalization. The Boltzmann equation is discretized both in space $\vec{x}$ and time $t$. Also, the velocity is limited to discrete values $\vec{c}_i$, the so-called velocity sets. The velocity sets are usually denoted as D$d$Q$q$, with $d$ being the number of dimensions and $q$ being the number of discrete velocities. The density is split into the so-called populations $f_i\left(\vec{x}, t\right)$, which are parts of the density moving along a certain discrete velocity at a certain discrete point in time at a certain discrete point in space. With these discretizations the equation reads as follows.

@@

	Here $\Delta t$ is the duration of a time step (distance between the discrete points in time) and $\Omega_i\left(\vec{x}, t\right)$ is the collision operator. The equation describes the populations moving along the discrete velocities to a neighboring point (streaming) while exchanging momentum modeled by the collision operator (collision). The collision operator redistributes the populations, that meet at any given lattice point. This is highly complex and is therefore usually approximated using the Bhatnagar-Gross-Krook (BGK) operator, which reads as follows.

@@

	It should be noted, that this is the simple case for a Newtonian fluid. If additional (extern) forces are to be considered, additional terms are added on the right-hand side to account for these. For simple forces we use the algorithm presented by Guo et al. \cite{guo2002}. The following equations relate the discrete quantities back to the physical quantities.

@@

	Here $\eta$ is the viscosity. These equations are typically solved in lattice units (LU). These result from fixing three values in LU and calculating conversion factors for all other units accordingly from these. The physical values are then divided by these scaling factors. This is mathematically identical to scaling the whole equation and can be used to simplify the calculations and to keep the values in a range optimal for computation. Typically, one picks $\rho_\text{LU} = 1$ and $\eta_\text{LU} = \frac{1}{6}$. Naturally $\Delta x_\text{LU} = 1$ and $\Delta t_\text{LU} = 1$. A convenient third scale is the resolution, meaning the relation of $\Delta x$ to the size of the system. The relaxation time can be freely chosen, but is ideal at unity in LU.
	The LBM scheme with the BGK operator is called single relaxation time (SRT). There are generalizations for two relaxation times (TRT) and for one relaxation time per $i$ (multi relaxation time, MRT). We found the more complex schemes to rarely yield worthwhile improvement and stick to SRT. While there are multiple valid options we use D3Q19 as the velocity set. The 19 velocities and their weights are noted in the following.

>>>>

To understand the rheology of such complex liquids in non-trivial geometries, computer simulations are an invaluable tool.
While a number of numerical techniques have been developed, the simulation of viscoelastic liquids remains an involved subject \cite{Alves.2020}, in particular for high viscosity ratios.
A very popular simulation technique for Newtonian fluids is the Lattice Boltzmann method (LBM) \cite{Kruger_book} due to its simplicity and high parallelizability.
LBM has also been extended to viscoelastic situations, mainly in two \cite{ispolatov2002,wang2019,su2013,giraud1998,xie2018,dzanic2022,frank2006,zou2014,lee2017,dzanic2022_2,sedaghat2021,frantziskonis2011,qin2023,yoshino2008,papenkort2015,phillips2011,onishi2005} but occasionally also in three \cite{malaspinas2010,gupta2015,gupta2015_2,lallemand2003,ma2020,onishi2006,wang2020,dellar2014,su2013_2,wang2021,kuron2021,gupta2016} dimensions.
\RR{We will discuss these approaches in detail in section~\ref{sec:existingLBM} below.}
To alleviate stability problems, some of these works include an artificial diffusivity of the polymer stress \cite{malaspinas2010,ma2020,wang2020,wang2021}, or perform special decompositions of the stress tensor \cite{dzanic2022}.
Despite these improvements, however, none of these methods has been applied to very high viscosity ratio fluids which are often used as cell carrier fluids in lab experiments or technological applications.

@@

We introduce the ratio between the polymer and the solvent viscosity \RR{and express it as a ratio between the viscosity at zero shear rate, $ \eta _0$, and the viscosity at infinite shear rate $ \eta _ \infty $}:
\begin{align}
	R_\eta = \frac{\eta_\text{p}}{\eta_\text{s}} = \frac{\eta_0-\eta_\infty}{\eta_\infty}		\label{eq:R_eta}
\end{align}
which we and others found to be an important parameter to determine numerical stability of LB simulations, especially if no artificial diffusivity is used \cite{malaspinas2010,dzanic2022_2}.
This ratio can similarly be defined for other models such as FENE-P or the inelastic, but shear-thinning Carreau-Yasuda model \cite{carreau1972, yasuda1979} using the zero-shear viscosity $\eta_0$ and the infinite-shear viscosity $\eta_\infty$.
For our alginate solution we obtain $R_\eta = \num{48.2\pm0.4e3}$, indicating that the solution viscosity at very low shear rates is more than four orders of magnitude larger than the solvent viscosity which represents a severe challenge to standard numerical algorithms.
That this characteristic is not unique to alginate, but is in fact a generic feature of cell carrier fluids used in bioprinting is shown in table~\ref{tab:bioinks} where rheological data from various literature sources have been compiled into a single format to determine $R_\eta$.
The \SI{0.49}{\percent} methyl cellulose solution used in RT-DC measurements, in contrast, features a much lower value of $R_\eta = \num{18.7\pm0.4}$.

@@

\section{Existing LBM methods}
\label{sec:existingLBM}
Since the early days of LBM, variants for viscoelastic fluids have been developed.
Keeping in mind our target geometries, we focus here on three-dimensional formulations.
The first approaches avoided an explicit modeling of a viscoelastic constitutive equation and simply modified the LB collision operator to obtain a basic viscoelastic fluid obeying Jeffery's model \cite{lallemand2003}. This can also be achieved by the introduction of a second local stress tensor \cite{dellar2014}.
More advanced approaches include the work of Onishi \textit{et al.} \cite{onishi2005, onishi2006} who considered a non-shear-thinning Oldroyd-B model using a microscopic Fokker-Planck equation for the polymer dumbbells.
The work of \cite{wang2020} solved the advection part of the model using a second LBM running in parallel to the Navier-Stokes LBM.
The same technique was used by \cite{malaspinas2010} and \cite{ma2020} for the Oldroyd-B and FENE-P models.
Later, hybrid schemes coupling an LB solver for the solvent to a finite-difference \cite{gupta2015_2, gupta2015, gupta2016} or finite-volume \cite{kuron2021} scheme for the polymer stress (or, alternatively, the polymer conformation) tensor were introduced.
To improve numerical stability, some authors propose the inclusion of an artificial diffusivity \cite{malaspinas2010,ma2020,wang2020,wang2021}, which introduces a small error compared to the analytical solution of the constitutive equation.
Others perform special decompositions of the stress tensor\cite{dzanic2022}.
Coupling of the resulting polymer stress to the Navier-Stokes LBM can be achieved via the inclusion of point forces or via a modification of the equilibrium populations.
Both methods have recently been compared in 2D \cite{dzanic2022_2}.

@@

The spatio-temporal dynamics of the polymer stress $\ma{\tau}$ is given by equation~(\ref{eq:polymerStress}) in the form of an advection-reaction equation.
We solve this equation by a finite-volume scheme running in parallel (with identical time step) to the LBM solver.\RR{ For this, the simulation volume is subdivided in $1\times1\times1$ (in LU) cubes centered around each lattice node. The average value of $\ma{\tau}$ within these volumes is takes as the value at the lattice node.}
Advection is handled using the corner transport upwind scheme \cite{kuron2021}. \SG{ add two phrases about CTU which somewhat non-standard }
\RR{ The remaining derivatives are calculated using finite differences.} 
At the walls\RR{, which coincide with the surfaces of the finite volumes}, a zero-flux boundary condition for the stress is used.
The source terms are integrated using the Euler method.

@@

We start by simulating the alginate and \SI{0.49}{\percent} methyl cellulose solutions with a viscosity ratio $R_\eta = \num{48.2e3}$ and $R_\eta = \num{18.7}$, respectively, in 2D planar Poiseuille flow.
In physical units the channel has a height of \SI{20}{\micro\meter} which are discretized with 41 LBM nodes.
For the viscosity shuffling, we set $\alpha_\text{s} = 1$ here and check different values further below.
Along the flow direction, the channel is periodic, and the flow is driven by a pressure gradient of \SI{-1e7}{\pascal\per\meter} for alginate and  approximately \SI{-1.2e7}{\pascal\per\meter} for methyl cellulose.
The velocity field is initialized with zero.
For methyl cellulose, we simulate the full temporal evolution with the polymers starting in the unstretched configuration.
In the case of alginate, we speed up the convergence and start from a situation in which the polymers are pre-stretched. For this we calculate $\tau_{xx}$ and $\tau_{xy}$ using equations~(\ref{eq:tau_xx}) and (\ref{eq:PTTDerivation2}) using the $\dot{\gamma}$ calculated from equation~(\ref{eq:semiAnalyticGD_3D}). The polymer stress is then initialized using these values.
After \num{2e9} LBM time steps for alginate and \num{5e6} LBM time steps for methyl cellulose corresponding to approximately \SI{1.6}{\milli\second} and \SI{2.4}{\second} of physical time, respectively, the simulation is stopped and the flow field $u(y)$ is compared to the semi-analytical solution.
\RR{An artificial increase of the Reynolds number to reduce computational time is possible in principle, but is not employed here to bring out clearly the characteristics of our method.}
As shown in figure~\ref{fig:2Dvel}, very good agreement is found.
The time evolution of the center-line velocity is shown in figure~\ref{fig:2DTimeEvolution} of the appendix.
For a quantitative assessment, we compute the L2 error as follows.
\begin{equation}
	e_\text{L2} = \sqrt{\frac{\sum_i\left[\vec{u_i} - \vec{u}\left(y_i\right)\right]^2}{\sum_i\vec{u}\left(y_i\right)^2}}
\end{equation}
Using the simulated velocities $\vec{u_i}$ and the semi-analytical results $\vec{u}$. This gives \num{9e-4} and \num{1e-3} for alginate and methyl cellulose, respectively.
The spatially resolved L1 error defined as follows is shown in figure~\ref{fig:2DvelErr} in the appendix.
\begin{equation}
	e_\text{L1} = \frac{\vec{u_i} - \vec{u}\left(y_i\right)}{\vec{u}\left(y_i\right)}
\end{equation}
These conclusions remain unchanged even when varying the pressure gradient, and thus the flow velocity, over many orders of magnitude as shown in figure~\ref{fig:pressureErr}~(a) of the appendix.
Similarly, the exact value of $\alpha_\text{s}$ does not matter as can be seen in figure~\ref{fig:ShuffleInPoiseuille}.

@@

Our next example is the RT-DC geometry in which cells from a reservoir are squeezed through a narrow observation channel \cite{Toepfner.2018, Fregin:2019gx} with a square cross-section of %\qtyproduct{40x40}{\micro\meter}.
%$\SI{40}{\micro\meter} \times \SI{40}{\micro\meter}$.%Correctly typeset version, that compiles for Stephan.
For this simulation we use periodic boundary conditions and a constant body force corresponding to a pressure gradient of \SI{1e7}{\pascal\per\meter}.
In figure~\ref{fig:RT-DC}, we show the velocity profile, the von Mises stress and the shear component of the stress which is the relevant component if a local shear viscosity is to be defined.
There are three qualitative differences compared to a purely viscous fluid.
Directly after the inlet we find a region of low stress.
Due to the fast advection, the polymers, despite being inside the constriction, have not reacted to the increased fluid stress yet.
Similarly, directly after the constriction, the high stress inside the observation channel persists over a certain distance that is needed for the polymer stress to decay. If one would divide the stress in these two regions by the strain rate in an attempt to obtain a viscosity one would find a very low and a very high viscosity respectively. These can be outside the range of viscosities, that can be obtained through rheological measurements with the fluid. This effect is even more pronounced along the walls directly after the outlet. Here the viscosities obtained in this manner become negative. Due to the strain rate approaching $0$ at several locations within the simulation volume, this calculation often diverges. The clamped result can be seen in figure~\ref{fig:Nozzle/RT-DC_eta}. These discrepancies, especially the ones at the walls, show the breakdown of the viscosity interpretation in viscoelastic cases and signify the regions of interesting behavior. This also shows why viscoelastic simulations cannot always be replaced by purely viscous models and should be considered despite the high computational cost.

@@

	\section{Lattice-Boltzmann Implementation}\label{app:LBM}
	An excellent overview on Lattice-Boltzmann methods (LBM) can be found in the book by Krüger et al. on the subject \cite{Kruger_book}. 
	Our implementation mostly follows the book, though some implementation details differ. 
	We mention the most important basics of LBM here and recommend the book for further reading.
	Instead of solving the Navier-Stokes equation LBM solves the Boltzmann equation for fluid particle distributions. 
	The Boltzmann equation is discretized both in space $\vec{x}$ and time $t$. 
	Also, the velocity is limited to discrete values $\vec{c}_i$, the so-called velocity sets. 
	The velocity sets are usually denoted as D$d$Q$q$, with $d$ being the number of dimensions and $q$ being the number of discrete velocities. 
	The density is split into the so-called populations $f_i\left(\vec{x}, t\right)$, which are parts of the density moving along a certain discrete velocity at a certain discrete point in time at a certain discrete point in space. 
	With these discretizations the Boltzmann equation reads as follows.

@@

	Here $\Delta t$ is the duration of a time step (distance between the discrete points in time) and $\Omega_i\left(\vec{x}, t\right)$ is the collision operator. 
	The equation describes the populations moving along the discrete velocities to a neighboring point (streaming) while exchanging momentum modeled by the collision operator (collision). 
	The collision operator redistributes the populations, that meet at any given lattice point. 
	This is highly complex and is therefore usually approximated using the Bhatnagar-Gross-Krook (BGK) operator, which reads as follows.

@@

	It should be noted, that this is the simple case for a Newtonian fluid. 
	If additional (external) forces are to be considered, additional terms are added on the right-hand side to account for these. 
	For simple forces we use the algorithm presented by Guo et al. \cite{guo2002}.  \SG{ what are ''simple forces''? }
	The following equations relate the discrete quantities back to the physical quantities.

@@

	Here $\eta$ is the viscosity. 
	These equations are typically solved in lattice units (LU). 
	These result from fixing three values in LU and calculating conversion factors for all other units accordingly from these. 
	The physical values are then divided by these scaling factors. 
	This is mathematically identical to scaling the whole equation and can be used to simplify the calculations and to keep the values in a range optimal for computation. 
	Typically, one picks $\rho_\text{LU} = 1$ and $\eta_\text{LU} = \frac{1}{6}$. 
	Naturally $\Delta x_\text{LU} = 1$ and $\Delta t_\text{LU} = 1$. 
	A convenient third scale is the resolution, meaning the relation of $\Delta x$ to the size of the system. 
	The relaxation time can be freely chosen, but is ideal at unity in LU.
	The LBM scheme with the BGK operator is called single relaxation time (SRT). 
	There are generalizations for two relaxation times (TRT) and for one relaxation time per $i$ (multi relaxation time, MRT). 
	We found the more complex schemes to rarely yield worthwhile improvement and stick to SRT. 
	While there are multiple valid options we use D3Q19 as the velocity set. 
	The 19 velocities and their weights are noted in the following.
